AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-17 Latex/Paper/main.tex
Finished conclusion and discussion.

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
context, problem, use cases
definitions
paper overview

@@

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
literature review, state of the art

@@

\section{algorithm overview and description}
\label{sec:algo}

@@

The implementation of our algorithm was done in Python using the numpy/scipy library stack. 
As well as the library nimfa\footnote{\url{http://nimfa.biolab.si/}} for NMF calculations.
The entire code repository is licensed under the GPL 3.0 and can be found on GitHub\footnote{\url{https://github.com/Bendrien/AudioContentAnalysis}}.

@@

As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
The data set contains recordings of 207 drum tracks split over 3 different drum kits.
In the data set each instrument of the drum kit is recorded separately.
For our purposes we only uses the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
Next to the recordings the test data set also contains a annotation file for each drum track, which lists the occurrence an instrument as well as the time point it occurred.
This data was used as the ground truth to compare our algorithm against.

In order to evaluate the accuracy of our algorithm we compared the drum events that our algorithm detected with the annotations of the ENST test set.
When comparing the results we took into account the epsilon error margin of approx. 12 ms.

  \begin{table}[h]
    \centering
    \begin{tabular}{l | c c c}
      Drummer  &  1 & 2 & 3 \\
      \# Files &   63 &   75 & 69 \\
      \hline
      Median$_{P}$   & 0.25 & 0.93 & 0.86 \\
      Mean$_{P}$     & 0.27 & 0.89 & 0.80 \\
      $\sigma_P$     & 0.22 & 0.12 & 0.18 \\
      \hline
      Median$_{FP}$   & 0.13 & 0.0 & 0.0 \\
      Mean$_{FP}$     & 0.23 & 0.0 & 0.001 \\
      $\sigma_{FP}$   & 0.29 & 0.0 & 0.001 \\
    \end{tabular}
    \caption{Results of the base drum detection. $P$ represents the true positives and $FP$ the false positives.}
    \label{tab:results}
  \end{table}

ground truth, methodology, metrics
results
discussion

- we only uses drum tracks, but it also works with mixed music. problem: ground truth

@@

summary, noteworthy parts of the presented work,
achievements and contributions
possible improvements and future work

Improvements: 
- Using adaptive templates like shown in \cite{lerch2015} can help the "over-fitting" of a template.
- adaptive threshold instead of 2/3
- sinc interpolation to reduce epsilon

>>>>

%\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
%context, problem, use cases
%definitions
%paper overview

@@

%\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
%literature review, state of the art

@@

\section{Algorithm overview and description}
\label{sec:algo}

@@

The implementation of our algorithm was done in Python using the numpy/scipy library stack. 
As well as the library nimfa\footnote{NMF library: \url{http://nimfa.biolab.si/}} for NMF calculations.
The entire code repository is licensed under the GPL 3.0 and can be found on GitHub\footnote{Repository: \url{https://github.com/Bendrien/AudioContentAnalysis}}.

@@

As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{ENST drum test database: \url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
The data set contains recordings of 207 drum tracks split over 3 different drum kits.
In the data set each instrument of the drum kit is recorded separately.
For our purposes we only uses the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
Next to the recordings the test data set also contains a annotation file for each drum track, which lists the occurrence an instrument as well as the time point it occurred.
This data was used as the ground truth to compare our algorithm against.

In order to evaluate the accuracy of our algorithm we compared the drum events that our algorithm detected with the annotations of the ENST test set.
When comparing the results we took into account the epsilon error margin of approx. 12 ms.
This leaves us with a detection rate for each track.
To get an overall estimate of the accuracy of our algorithm we calculated the median for each drum kit as well as the mean and the standard deviation.
Besides the true positives we also counted the false positives for each track, where our algorithm would detect a drum event, but according to the annotations there is none there.
We calculated the median, mean and standard deviation across all tracks for the false positives as well.
The results of our evaluation for the base drum template can be found in table \ref{tab:results}.

\begin{table}[h]
  \centering
  \begin{tabular}{l | c c c}
      Drum kit  &  1 & 2 & 3 \\
      \# Files &   63 &   75 & 69 \\
      \hline
      Median$_{P}$   & 0.25 & 0.93 & 0.86 \\
      Mean$_{P}$     & 0.27 & 0.89 & 0.80 \\
      $\sigma_P$     & 0.22 & 0.12 & 0.18 \\
      \hline
      Median$_{FP}$   & 0.13 & 0.0 & 0.0 \\
      Mean$_{FP}$     & 0.23 & 0.0 & 0.001 \\
      $\sigma_{FP}$   & 0.29 & 0.0 & 0.001 \\
  \end{tabular}
  \caption{Results of the base drum detection. $P$ represents the true positives and $FP$ the false positives.}
  \label{tab:results}
\end{table}

As visible in table \ref{tab:results} the results for drum kit 2 are the best with a average of around 90\% accuracy and a fairly low standard deviation.
The same is true for drum kit 3 which had a detection rate in the mid 80's.
Both had none or close to no false positives.
Drum kit 1 shows different accuracy results.
Here only around 25\% of the base drum hits are detected correctly, while the false positive detection is also at around 20\%.
The standard deviation is also significantly higher.

From these results we can see that our algorithm returns very satisfying results for 2 out 3 drum kits from our test data set.
We also found an explanation for the outlier.
When listening to the base drum sounds of the individual drum kits it becomes obvious that drum kit 2 and 3 sound very alike with a sharp, crisp base drum sound, while the drum kit 1 sounds more smooth and mellow.
Since the base drum template used here was extracted from the drum kit 2 it is not very surprising that the algorithm can't find it in the much different sounding drum kit 1.
The solution to this problem would be to use a more generalized base drum template.
This shows an apparent flaw in the design of the algorithm.
It can only work as good as the templates it is provided with.
If the sound the algorithm is looking for is pitched or distorted to much, it won't be picked up.
More on how to improve this work in section \ref{sec:conclusion}.

%ground truth, methodology, metrics
%results
%discussion

@@

In conclusions the algorithm returns surprising good results given its relative simplicity.
As with all pattern matching algorithms if the feature the algorithm is looking for differs to much from the provided template the accuracy declines, even if a human listener is still able to pick them out.
Work by Lerch et al. \cite{lerch2015} has shown that by introducing an additional step into the algorithm this problem can be mitigated.
The step is called template adaption and happens between the NMF and the onset detection in figure \ref{fig:Flowchart}.
Through different methods described in their paper it is possible to iteratively adapt the template to the detections in the music.
That way an ``over-fitting'' of the template to a certain drum kit can be avoided.

Another area of improvement is the onset detection with special focus on the peak picking algorithm.
Here the empirically chosen threshold value of $\frac{2}{3}$ already yield good results, but it is also responsible for some missed events and some false positives.
Using an adaptive threshold would further improve the outcome.

As mentioned above he precision of the detected peak time point is is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.

Originally we wanted to test our drum transcription algorithm on a piece of mixed polyphonic music instead of just drum tracks.
Sadly we were unable to find an annotated test data set that fit our needs as a ground truth.
Theoretically by using mixed music only the activation matrix $\mathbf{H}$ should get a bit more noisy.
Everything else should work as described here.

In closing we have presented an algorithm in this paper that gives satisfying results when trying to extract the exact time points at which base drum hits happen in a drum track.
It can easily be extended to other percussive instruments and maybe even other melodic instruments.
The accuracy and precision could be improved in future work by the methods mentioned.

%summary, noteworthy parts of the presented work,
%achievements and contributions
%possible improvements and future work
